Towards End-User Web Scraping for Customization

### 2021-06-09 paper.tex
Made changes recommended by conference publishing

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,10pt]{acmart}

@@

\usepackage{hyperref}

@@

%%% The following is specific to <Programming'21> Companion-PX and the paper
%%% 'Towards End-User Web Scraping for Customization'
%%% by Kapaya Katongo, Geoffrey Litt, and Daniel Jackson.
%%%
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3464432.3464437}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{prog21pxmain-p5-p}
\acmISBN{978-1-4503-8986-0/21/03}
\acmConference[<Programming'21> Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming'21> Companion), March 22--26, 2021, Virtual, UK}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Towards End-user Web Scraping For Customization}

@@

\hypertarget{creating-an-adapter}{%
\subsection{Creating An Adapter}\label{creating-an-adapter}}

@@

\hypertarget{extending-an-adapter}{%
\subsection{Extending An Adapter}\label{extending-an-adapter}}

@@

\hypertarget{repairing-an-adapter}{%
\subsection{Repairing An Adapter}\label{repairing-an-adapter}}

@@

\hypertarget{editing-by-demonstration}{%
\subsection{Editing By Demonstration}\label{editing-by-demonstration}}

@@

\hypertarget{data-loaded-after-initial-render}{%
\subsubsection{Data Loaded After Initial
Render}\label{data-loaded-after-initial-render}}

@@

\hypertarget{editing-by-demonstration-1}{%
\subsection{Editing By Demonstration}\label{editing-by-demonstration-1}}

@@

\hypertarget{end-user-web-scraping}{%
\subsection{End-user Web Scraping}\label{end-user-web-scraping}}

@@

\hypertarget{end-user-web-customization}{%
\subsection{End-user Web
Customization}\label{end-user-web-customization}}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references-bibtex.bib}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen]{acmart}

@@

\usepackage{hyperref}
\usepackage{microtype}
\usepackage{balance}

@@

%%% The following is specific to <Programming> '21 Companion-PX and the paper
%%% 'Towards End-User Web Scraping for Customization'
%%% by Kapaya Katongo, Geoffrey Litt, and Daniel Jackson.
%%%
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3464432.3464437}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{prog21pxmain-p5-p}
\acmISBN{978-1-4503-8986-0/21/03}
\acmConference[<Programming> '21 Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming> '21 Companion), March 22--26, 2021, Virtual, UK}

\pagenumbering{gobble}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Towards End-User Web Scraping for Customization}

@@

\hypertarget{creating-an-adapter}{%
\subsection{Creating an Adapter}\label{creating-an-adapter}}

@@

\hypertarget{extending-an-adapter}{%
\subsection{Extending an Adapter}\label{extending-an-adapter}}

@@

\hypertarget{repairing-an-adapter}{%
\subsection{Repairing an Adapter}\label{repairing-an-adapter}}

@@

\hypertarget{editing-by-demonstration}{%
\subsection{Editing by Demonstration}\label{editing-by-demonstration}}

@@

\hypertarget{data-loaded-after-initial-render}{%
\subsubsection{Data Loaded after Initial
Render}\label{data-loaded-after-initial-render}}

@@

\hypertarget{editing-by-demonstration-1}{%
\subsection{Editing by Demonstration}\label{editing-by-demonstration-1}}

@@

\hypertarget{end-user-web-scraping}{%
\subsection{End-User Web Scraping}\label{end-user-web-scraping}}

@@

\hypertarget{end-user-web-customization}{%
\subsection{End-User Web
Customization}\label{end-user-web-customization}}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\balance
\bibliography{references-bibtex.bib}
